Machine Learning guided Design\\ of Ribosome Binding Sites

### 2021-06-15 paper/main.tex
mengyan edit on abstract and discussion

In \ref{fig: Swarmplot and Quantplot}E we show a t-SNE plot depicting the experimental space.
Each RBS is located on the plot according to its distance from other RBSs as calculated by our embedding function.
The RBSs recommended by Bandit groups have covered majority of the design space. 
Additionally, a number of clusters were especially targeted by our recommendation algorithm.
For example, the circled clusters labelled as ``G-Rich Clusters" have been actively recommended by the algorithm.
More specifically, sequences with more or equal to 4 guanines in any position constituted 10\% of the randomly selected sequences and 5, 9, 16 and finally 25\% in each of the 4 Bandit guided batches respectively.

>>>>

In \ref{fig: Swarmplot and Quantplot}E we show a t-SNE plot depicting the experimental space.
Each RBS is located on the plot according to its distance from other RBSs as calculated by our embedding function.
The RBSs recommended by Bandit groups have covered majority of the design space. 
Additionally, a number of clusters were especially targeted by our recommendation algorithm.
For example, the circled clusters labelled as ``G-Rich Clusters" have been actively recommended by the algorithm.
More specifically, sequences with 4 or more guanines in any position constituted 10\% of the randomly selected sequences and 5, 9, 16 and finally 25\% in each of the 4 Bandit guided batches respectively.
